### 2017-05-12 paper/evaluation.tex
pass on scalability

The dimension adoption focuses on the usage of parallelism in
open-source projects.  It evaluates (\numRQAdoptionOne) how often open-source
projects use parallelization schemes and (\numRQSpeedupOne) how developers
involved in costly projects, not using parallelization, perceive this
technology.

@@

\begin{figure}[h!]
\centering
\resizebox{.41\textwidth}{!}{%
  \scriptsize
\begin{tabular}{llrrr}
\toprule
\emph{Group} & \emph{Subject} & \multicolumn{1}{c}{$T_s$} & \multicolumn{1}{c}{$T_p$} & $T_s/T_p$ \\%
\midrule%
Medium & \Comment{BounceStorage }Chaos\Comment{ HTTP Proxy} & 1.51m & 1.47m & 
    \cellcolor{lightgray}1.01x\\%
Medium &\Comment{ Apache }Flink& 11.79m & 2.57m & 4.59x\\%
Long &\Comment{ Jenkins CI }Gerrit\Comment{ Plugin} & 51.19m & 40.31m &  1.26x\\%
Medium &\Comment{ Spotify }Helios& 4.46m & 1.63m & 2.73x\\%  
Medium &Javaslang& 2.18m & 1.82m & 1.19x\\%
Medium &Jcabi\Comment{ GitHub} & 2.76m & 0.30m &
    \cellcolor{lightgray}9.2x\\%
Medium &\Comment{ Hazelcast }Jet& 8.26m & 3.67m & 2.25x\\%
Long &\Comment{ Apache }Log4J2& 8.24m & 8.21m & \cellcolor{lightgray}1.00x\\%
Long &\Comment{ Jankotek }MapDB& 10.06m & 8.58m & 1.17x\\%
\midrule
\textbf{average} &  &  &  & \avgSpeedup{}x\\
\bottomrule%
\end{tabular}}
\caption{Speedup (or slowdown) of parallel execution ($T_p$) over
  sequential execution ($T_s$).  Default parallel configuration of
  Maven is used.  Highest slowdown/speedup appears in gray color.}
\label{tab:speedup}
\end{figure}

@@

>>>>

The dimension adoption focuses on the usage of parallelism in
open-source projects.  It evaluates (\numRQAdoptionOne) how often open-source
projects use parallelization schemes and (\numRQAdoptionTwo) how developers
involved in costly projects, not using parallelization, perceive this
technology.

@@

\begin{figure}[h!]
\centering
\resizebox{.41\textwidth}{!}{%
  \scriptsize
\begin{tabular}{llrrr}
\toprule
\emph{Group} & \emph{Subject} & \multicolumn{1}{c}{$T_s$} & \multicolumn{1}{c}{$T_p$} & $T_s/T_p$ \\%
\midrule%
Medium & \Comment{BounceStorage }Chaos\Comment{ HTTP Proxy} & 1.51m & 1.47m & 
    \cellcolor{lightgray}1.01x\\%
Medium &\Comment{ Apache }Flink& 11.79m & 2.57m & 4.59x\\%
Long &\Comment{ Jenkins CI }Gerrit\Comment{ Plugin} & 51.19m & 40.31m &  1.26x\\%
Medium &\Comment{ Spotify }Helios& 4.46m & 1.63m & 2.73x\\%  
Medium &Javaslang& 2.18m & 1.82m & 1.19x\\%
Medium &Jcabi\Comment{ GitHub} & 2.76m & 0.30m &
    \cellcolor{lightgray}9.2x\\%
Medium &\Comment{ Hazelcast }Jet& 8.26m & 3.67m & 2.25x\\%
Long &\Comment{ Apache }Log4J2& 8.24m & 8.21m & \cellcolor{lightgray}1.00x\\%
Long &\Comment{ Jankotek }MapDB& 10.06m & 8.58m & 1.17x\\%
\midrule
\textbf{average} &  &  &  & \avgSpeedup{}x\\
\bottomrule%
\end{tabular}}
\caption{\label{tab:speedup}Speedup (or slowdown) of parallel
  execution ($T_p$) over sequential execution ($T_s$).  Default
  parallel configuration of Maven is used.  Highest slowdown/speedup
  appears in gray color.}
\end{figure}

@@

\newcommand{\subjectScalability}{MapDB}

This experiment evaluates the impact of making available to the build
system a growing number of CPUs for testing.  For that reason, we used
a \Fix{...describe machine...}  We focused on configuration \ForkSeq{}
\begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth
    \centering
    \includegraphics[width=.2\textwidth]{R/scalability/scalability.pdf}
    \caption{\label{fig:scalability}Scalability.}
\end{wrapfigure}
as the goal is to evaluate the impact of spawning a growing number of
JVMs, running on different CPUs.  We selected the subject
\subjectScalability{} in this experiment as it represents the case of
a long-running test suite (see Figure~\ref{tab:speedup}) distributed
across many test classes (\Fix{X} test classes for
\subjectScalability{}).  Note that a test class is the smallest unit
that can be used to spawn a test job on a JVM.

Figure~\ref{fig:scalability} shows the reduction of running times as
more CPUs contribute to the execution.  \Fix{elaborate...}
